\chapter{Industrial Tools}
Some industrials tools related to analog layout generation will be reviewed in this following part.
\begin{itemize}
\item Synopsys Helix (ex-Ciranova since 2012) cite{27} is a device-level automated placement solution for analog, and mixed-signal IC designs such as PLLs, SerDes, ADCs and PHYs. Helix is fully hierarchical and offers capacity in the tens of thousands of transistors, enabling it to optimize floorplanning and placement for
entire custom IC blocks or IP at once.
\item Mentor Graphics Pyxis Layout Suite cite{28} offers configured options for design engineers who need increased productivity and an automated way of handling the physical layout of their AMS designs. Bundles are offered in a standard configuration, with optional applications that provide increasing levels of automation and functionality to address the designers unique requirements.
\item Synopsys Laker cite{29} delivers a complete solution for analog, mixed-signal, and custom digital design and layout that is optimized for performance and interoperability for 28-nanometer (nm) and below design flows. It has a built-in understanding of analog layout requirements, so it is much easier to adopt and deploy than competing analog automation tools.
\item Virtuoso Layout Suite Family cite{30} comprises the layout environment of the industry-standard Virtuoso custom design platform, a complete solution for front-to back custom analog, digital, RF, and mixed-signal design. It preserves design intent throughout the entire physical implementation process, while managing multiple levels of design abstractions from device, cell, and block levels through to the full-chip level.
\item Tanner EDA - High Performance Device Generation (HiPer DevGen) cite{31} creates building blocks based on an understanding of the functional requirements that are needed to produce a high-quality layout. Retargeting the components to a new technology node simply requires the user to input the manufacturing rules for that technology and regenerate the devices and primitives.
\end{itemize}